Analysing Constraint Grammars with a SAT-solver

### 2016-02-16 paper/lrec/eval_futurework.tex
fix typos; separate eval and future work in different sections

\section{Evaluation and Future Work}
\label{sec:eval}

@@

\paragrahp{Spanish} The Spanish grammar had proportionately the highest number of errors.\footnote{TODO://link/to/error.log} \todo{confirm; I assume this is gonna be so, but let's see Fin & Por}.  The grammar we ran is like the one found in the Apertium repository, apart from 2 changes: we fixed some typos (capital O for 0) in order to make it compile, and commented out two rules that used regular expressions, because our solution does not handle them properly (see more on Future work/Implementation).

@@

\paragrahp{Finnish} \todo{Rerun the tests & rewrite this whole section!} For the Finnish grammar, we did not have time to investigate all the
results. We could verify approximately \nicefrac{1}{3} as true positives and
\nicefrac{1}{3} as false positives.
The verified true positives were all rule-internal conflicts. 
For example, the following rule requires the target to be genitive and unambiguously nominative: 
\begin{itemize}
\item[]\texttt{"oma" SELECT GEN IF [...] (0C NOM) ;}
\end{itemize}
We also detected a number of tagset errors;
the grammar was originally written in 1995, and converted to the
Omorfi tagset by \cite{pirinen2015}, but there were 15 rules that used the old convention for possessive suffixes.

@@

\paragraph{Future work}

>>>>

\section{Evaluation}
\label{sec:eval}

@@

\paragraph{Spanish} The Spanish grammar had proportionately the highest number of errors.\footnote{TODO://link/to/error.log} \todo{confirm; I assume this is gonna be so, but let's see Fin and Por}.  The grammar we ran is like the one found in the Apertium repository, apart from 2 changes: we fixed some typos (capital O for 0) in order to make it compile, and commented out two rules that used regular expressions, because our solution does not handle them properly (see more on Future work/Implementation).

@@

\paragraph{Finnish} \todo{Rerun the tests and rewrite this whole section!} For the Finnish grammar, we did not have time to investigate all the
results. We could verify approximately \nicefrac{1}{3} as true positives and
\nicefrac{1}{3} as false positives.
The verified true positives were all rule-internal conflicts. 
For example, the following rule requires the target to be genitive and unambiguously nominative: 
\begin{itemize}
\item[]\texttt{"oma" SELECT GEN IF [...] (0C NOM) ;}
\end{itemize}
We also detected a number of tagset errors;
the grammar was originally written in 1995, and converted to the
Omorfi tagset by \cite{pirinen2015}, but there were 15 rules that used the old convention for possessive suffixes.

@@

\section{Future work}
